MG7: Configurable and scalable 16S metagenomics data analysis -- new methods optimized for massive cloud computing

### 2015-09-13 docs/paper/out/paper.tex
add who did what to libraries -- paper

\href{https://github.com/ohnosequences/statika}{Statika} is a Scala
library developed by \textbf{so and so} which serves as a way of
defining and composing machine behaviors statically. The main component
are \textbf{bundles}. Each bundle declares a sequence of computations
(its behavior) which will be executed in an \textbf{environment}. A
bundle can \emph{depend} on other bundles, and when being executed by an
environment, its DAG of dependencies is linearized and run in sequence.
In our use, bundles correspond to what an EC2 instance should do and an
environment to an image (AMI: \textbf{A}mazon \textbf{M}achine
\textbf{I}mage) which prepares the basic configuration, downloads the
Scala code and runs it.

@@

\href{https://github.com/ohnosequences/datasets}{Datasets} is a Scala
library developed by \textbf{so and so} to declare datasets and their
locations. \textbf{Data} is represented as type-indexed fields: Keys are
modeled as singleton types, and values correspond to what could be
called a denotation of the key: a value of type \texttt{Location} tagged
with the key type. Then a \textbf{Dataset} is essentially a collection
of data, which are guaranteed statically to be different through
type-level predicates, making use of the value ↔ type correspondence
which can be established through singleton types and implicits. A
dataset location is then just a list of locations formed by locations of
each data member of that dataset.

@@

\href{https://github.com/ohnosequences/loquat}{Loquat} is a library
developed by \textbf{so and so} designed for the execution of
embarrassingly parallel tasks using S3, SQS and EC2.

>>>>

\href{https://github.com/ohnosequences/statika}{Statika} is a Scala
library developed by the first and last authors which serves as a way of
defining and composing machine behaviors statically. The main component
are \textbf{bundles}. Each bundle declares a sequence of computations
(its behavior) which will be executed in an \textbf{environment}. A
bundle can \emph{depend} on other bundles, and when being executed by an
environment, its DAG of dependencies is linearized and run in sequence.
In our use, bundles correspond to what an EC2 instance should do and an
environment to an image (AMI: \textbf{A}mazon \textbf{M}achine
\textbf{I}mage) which prepares the basic configuration, downloads the
Scala code and runs it.

@@

\href{https://github.com/ohnosequences/datasets}{Datasets} is a Scala
library developed by the first and last authors to declare datasets and
their locations. \textbf{Data} is represented as type-indexed fields:
Keys are modeled as singleton types, and values correspond to what could
be called a denotation of the key: a value of type \texttt{Location}
tagged with the key type. Then a \textbf{Dataset} is essentially a
collection of data, which are guaranteed statically to be different
through type-level predicates, making use of the value ↔ type
correspondence which can be established through singleton types and
implicits. A dataset location is then just a list of locations formed by
locations of each data member of that dataset.

@@

\href{https://github.com/ohnosequences/loquat}{Loquat} is a library
developed by the first, second and last authors designed for the
execution of embarrassingly parallel tasks using S3, SQS and EC2.
